---
title: "Additional"
author: "John W. Hoggard"
date: "10/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
source("CleanData.R")
```

On your histogram of dates founded for the data science positions, I think the long leftward tail is indicative of the somewhat smaller number of companies that have been along for a long time, vs. a large number of firms that were more recently founded.  (Many companies may not last that long.) We are probably seeing what is known a *survivorship bias* here:

```{r}
jobs %>%
  ggplot(aes(x = Founded)) +
  geom_histogram(binwidth = 15) + 
  labs(title = "Most Jobs are at Recently Founded Firms", y = "Positions")
```

Here's your New York jobs, redone as a bar plot, and filtered to only show New York jobs:

```{r}
jobs %>%
    filter(Location == "New York, NY") %>%
    ggplot(aes(y = Size )) +
    geom_bar() +
    labs(title = "New York Data Science Jobs", subtitle = "By Size of Company", 
         x = "Jobs")
```

Your interactions graph would be improved with a regression line, which seems to (slightly) suggest the more recently founded companies have higher ratings:

```{r}
jobs %>%
    filter(!is.na(Founded), !is.na(Rating)) %>%
    ggplot(aes(x = Founded, y = Rating )) +
    geom_point() + 
    geom_smooth(method = "lm", se = F, formula=y~x) +
    labs(title = "Do More Recent Companies have Higher Ratings?")
```

